% Validation section should include: 
% Data/MC Agreement after precuts on all important variables
% Sideband Checks
% Corsika In-time vs BNB-ext
% Future Validation Studies

\section{Validation}

\subsection{Simulation/Data Comparisons}
In this section, show the plots for all variables going into background rejection cuts.  For each plot, show the POT-normalized version (stacked MC, data on top) and the unit-normalized version for MC for three different categories: BNB nues (signal), BNB NC/numu/etc (Beam induced backgrounds) and Cosmic induced backgrounds. \todo{Make these plots}

\subsection{Side-bands checks}

Show data/MC comparisons of final event rates with reversed cuts.  This should be less aggressive than the nue cuts to have higher statistics.

\subsubsection{Photon enhanced reverse cuts}
Move the dE/dx region to 3 to 5 MeV/cm, require a gap of some minimum distance between the vertex and the shower start
\todo{Photon enhanced sideband}

\subsubsection{CC $\nu_{\mu}$ enhanced reverse cuts}
Require track length greater than some value, maybe shower gap distance larger than some value.  Try to isolate the numu background that shows up in the selection a bit to understand it.
\todo{Numu sideband}

\subsection{CORSIKA in-time / EXT comparisons}

Compare Corsika to bnb ext data for preselection, cut variables (dE/dx, etc) to see if bnb ext and corsika in time agree.  Essentially, validating the cosmic-only part of the nue selection backgrounds
\todo{Corsika Intime / BNB Ext Comparisons}

\subsection{Future Validation Studies}

\subsubsection{Data/MC Comparisons with NuMI}
\todo{Fill out NuMI section with a plan, no plots needed.}
